### 2014-03-04 seminar/seminar_report/Abstract.tex
changes

Web services are loosely-coupled business applications willing to
cooperate in distributed settings within different groups called
communities. Communities aim to provide better visibility,
efficiency, market share and total payoff. There are a number of
proposed mechanisms and models on aggregating web services and
making them cooperate within their communities. However, forming
optimal and stable communities as coalitions to maximize
individual and group efficiency and income for all the involved
parties has not been addressed yet.

In this proposal, we identify the problem of defining efficient
algorithms for coalition formation mechanisms within communities
and propose preliminary results using cooperative game-theoretic
techniques. We propose a mechanism for community membership
requests and selections of web services in the scenarios where
there is interaction between one community and many web services
and scenarios where web services can join multiple established
communities. The ultimate objective is to develop a mechanism for
web services to form stable groups allowing them to maximize their
efficiency and generate near-optimal (welfare-maximizing)
communities. The theoretical and extensive simulation results show
that our algorithms provide web services and community owners, in
real-world like environments, with applicable and near-optimal
decision making mechanisms.

As remaining work in this thesis, we propose to apply different
cooperative game techniques such as nucleus, kernel and bargaining
solution concepts and theoretically analyze those solution
concepts based on functions representing payoff and quality
metrics of the communities. We also aim to apply reinforcement
learning techniques for individual web service strategic decision
making process.

>>>>

In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise. The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities. There are a number of proposed mechanisms and models on aggregating web services and making them cooperate within their communities. However, forming optimal and stable communities as coalitions to maximize individual and group efficiency and income for all the involved parties has not been addressed yet. Also, in the proposed frameworks of these communities, a common assumption is that residing services, which are supposed to be autonomous and intelligent, are competing over received requests, but also exhibit cooperative behaviors, for instance in terms of substituting each other.

In this report, we identify the problem of defining efficient algorithms for coalition formation mechanisms within communities and propose preliminary results using cooperative game-theoretic techniques. We propose a mechanism for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities. The ultimate objective is to develop a mechanism for web services to form stable groups allowing them to maximize their efficiency and generate near-optimal (welfare-maximizing) communities. The theoretical and extensive simulation results show that our algorithms provide web services and community owners, in real-world like environments, with applicable and near-optimal decision making mechanisms. We also propose a decision mechanism based on learning methods for services within communities to effectively choose the tasks to perform based on their capabilities and the competition between other community members.

### 2014-03-04 seminar/seminar_report/chapter1.tex
changes

\setcounter{chapter}{0}
%*******************************START INTRODUCTION **********************************
\chapter{Introduction}\label{sec:intro}
In this chapter, we introduce the context of this research, which
is about communities of web services abstracted as autonomous
agents. Those agent-based web services use cooperative game
theoretic solution concepts for decision making. We discuss the
motivations of this work and briefly review the literature to
identify the problems we aim to solve in this thesis. Moreover, we
discuss our objectives and preliminary contributions.

@@

>>>>

\setcounter{chapter}{0}
%*******************************START INTRODUCTION **********************************
\chapter{Introduction}\label{sec:intro}
%In this chapter, we introduce the context of this research, which
%is about communities of web services abstracted as autonomous
%agents. Those agent-based web services use cooperative game
%theoretic solution concepts for decision making. We discuss the
%motivations of this work and briefly review the literature to
%identify the problems we aim to solve in this thesis. Moreover, we
%discuss our objectives and preliminary contributions.

@@

Within communities, service providers can 
can have competitive behaviour as they provide the same functionalities and the number of users requests is finite. So as an extension to our work, we have implemented a framework in which service providers can opt for performing tasks if they feel they are capable enough.
We have implemented an online learning mechanism for service providers with different captaincies to learn over time which strategy to choose based on their own and other service providers status and capabilities. After establishing states of our model and observing convincing results from our learning method, we plan to extend the learning process using reinforcement learning (q-learning) techniques.

### 2014-03-04 seminar/seminar_report/chapter2.tex
changes

\section{Community of Web Services}\label{sec:CommunityWS}
In this section, we present web services and discuss the concept
of their communities from architectural and operations
perspectives.

\subsection{Web Services}\label{sec:CWSWebServices}

In our research work, we abstract web services as rational
agents\footnote{The term
        rational is used here in the sense that web services are utility
        maximizers} providing services to end users. They aim to maximize
        their individual income by receiving enough requests from end
        users. In order to increase their revenue, web services seek for
        more tasks if they have the capacity and throughput to do so. Web
        services can join communities to have better efficiency by
        collaborating with others, to have access to broad market share,
        and to have opportunity of receiving a bigger task pool from end
        users. Furthermore, the high reliance on web services has increased quality expectations from end users.
        Communities of web services can provide higher availability, performance, reliability, and recovery for end users.

\subsection{Web Service Communities}\label{sec:CWSDefinition}
 In \cite{DBLP:journals/internet/BenatallahSD03,
Zeng:2003:QDW:775152.775211}, the authors introduce community of
web services as collection of cooperative web services with common
functionalities but different QoS metrics. Therefore
$communities$ are differentiated from $composition$ types of web
service cooperation in which web services with different
functionalities work together to generate a new service with
composite functionality.

Maamar et al. in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities. This
architecture has been further developed in
\cite{conf/IEEEscc/BenharrefSBB11, conf/IEEEscc/KhosravifarBMMT10,
conf/aina/LimTM11, CSTintercommunity}. Two types of roles have
been distinguished for community members: masters and slaves.
Master web services lead communities and are responsible for
membership management. They can invite and convince slave web
services to join the community, and attract new slave web services
to their communities by awarding them better payoff. Moreover,
they can eject some slave members from the community to improve
its overall reputation if these members are misbehaving or cannot
provide the promised QoS \cite{DBLP:journals/ijebr/MaamarSTBB09}.

@@

            \subsubsection*{Coalition Structure Formation}\label{sec:coalition}

            Coalition structure formation is the problem of finding the best
            partition of web services into teams. In these settings, the
            performance of an individual service is less important than the
            \emph{social welfare} of the whole system, which is the sum of the
            values of all teams. Having the game $(N,v)$, a coalition
            structure $(CS)$ is \emph{socially optimal} if $CS$ belongs to set
            $\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS)$ is the sum of
            the values of all coalitions inside $CS$. $v(CS) = \sum_{C \in
            CS}v(C)$.
            %The outcome of a characteristic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.

        \subsection{Representation and Complexity Issues}\label{sec:CWSArchitecture}

        Shapely value is the unique ``fair'' way to distribute the total surplus generated by the coalition, among all the players.
        The nature of the Shapley value is combinatorial, as all possible orderings to form a
        coalition needs to be considered. This computational complexity can sometimes be
        an advantage as agents cannot benefit from manipulation. For example, it is NP-complete
        to determine whether for a bunch of agents to collude and make their own coalition and guarantee
        an increase in payoff of all participants \cite{conf/aaai/YokooCSOI05}.
        There are some representations that allow us to compute the Shapley value efficiently by reducing the input size of the problem.
        One example is \emph{Induced subgraph games}
        which was introduced by Deng and Papadimitriou \cite{Deng94}. In this representation, players are represented by graph nodes, and
        their valuation function should be the sum of weights of all edges between the node and all its neighbors. It is a succinct representation, using
        an adjacency matrix, which needs only $O(n^2)$ space to store all the input, which is a major improvement from $O(2^n)$ because
        if weights of all the edges in graph are all positive, the Shapley value can be computed in time $O(n^2)$.

        In order to make cooperative game concepts practical in real world application, we have proposed an approximation multi-layer
        algorithm useful for service oriented computing settings. Our excrements illustrate, these algorithms can provide
        applicable and near optimal solutions for real world applications.

>>>>

%\section{Community of Web Services}\label{sec:CommunityWS}
%In this section, we present web services and discuss the concept
%of their communities from architectural and operations
%perspectives.
%
%\subsection{Web Services}\label{sec:CWSWebServices}
%
%In our research work, we abstract web services as rational
%agents\footnote{The term
%        rational is used here in the sense that web services are utility
%        maximizers} providing services to end users. They aim to maximize
%        their individual income by receiving enough requests from end
%        users. In order to increase their revenue, web services seek for
%        more tasks if they have the capacity and throughput to do so. Web
%        services can join communities to have better efficiency by
%        collaborating with others, to have access to broad market share,
%        and to have opportunity of receiving a bigger task pool from end
%        users. Furthermore, the high reliance on web services has increased quality expectations from end users.
%        Communities of web services can provide higher availability, performance, reliability, and recovery for end users.
%
%\subsection{Web Service Communities}\label{sec:CWSDefinition}
% In \cite{DBLP:journals/internet/BenatallahSD03,
%Zeng:2003:QDW:775152.775211}, the authors introduce community of
%web services as collection of cooperative web services with common
%functionalities but different QoS metrics. Therefore
%$communities$ are differentiated from $composition$ types of web
%service cooperation in which web services with different
%functionalities work together to generate a new service with
%composite functionality.
%
%
%Maamar et al. in \cite{DBLP:journals/ijebr/MaamarSTBB09}
%proposed an architecture utilizing \emph{Contract-Net} protocol
%for engineering task distribution within communities. This
%architecture has been further developed in
%\cite{conf/IEEEscc/BenharrefSBB11, conf/IEEEscc/KhosravifarBMMT10,
%conf/aina/LimTM11, CSTintercommunity}. Two types of roles have
%been distinguished for community members: masters and slaves.
%Master web services lead communities and are responsible for
%membership management. They can invite and convince slave web
%services to join the community, and attract new slave web services
%to their communities by awarding them better payoff. Moreover,
%they can eject some slave members from the community to improve
%its overall reputation if these members are misbehaving or cannot
%provide the promised QoS \cite{DBLP:journals/ijebr/MaamarSTBB09}.

@@

%            \subsubsection*{Coalition Structure Formation}\label{sec:coalition}

            \emph{Coalition structure formation} is the problem of finding the best
            partition of web services into teams. In these settings, the
            performance of an individual service is less important than the
            \emph{social welfare} of the whole system, which is the sum of the
            values of all teams. Having the game $(N,v)$, a coalition
            structure $(CS)$ is \emph{socially optimal} if $CS$ belongs to set
            $\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS)$ is the sum of
            the values of all coalitions inside $CS$. $v(CS) = \sum_{C \in
            CS}v(C)$.
            %The outcome of a characteristic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.

%        \subsection{Representation and Complexity Issues}\label{sec:CWSArchitecture}
%
%        Shapely value is the unique ``fair'' way to distribute the total surplus generated by the coalition, among all the players.
%        The nature of the Shapley value is combinatorial, as all possible orderings to form a
%        coalition needs to be considered. This computational complexity can sometimes be
%        an advantage as agents cannot benefit from manipulation. For example, it is NP-complete
%        to determine whether for a bunch of agents to collude and make their own coalition and guarantee
%        an increase in payoff of all participants \cite{conf/aaai/YokooCSOI05}.
%        There are some representations that allow us to compute the Shapley value efficiently by reducing the input size of the problem.
%        One example is \emph{Induced subgraph games}
%        which was introduced by Deng and Papadimitriou \cite{Deng94}. In this representation, players are represented by graph nodes, and
%        their valuation function should be the sum of weights of all edges between the node and all its neighbors. It is a succinct representation, using
%        an adjacency matrix, which needs only $O(n^2)$ space to store all the input, which is a major improvement from $O(2^n)$ because
%        if weights of all the edges in graph are all positive, the Shapley value can be computed in time $O(n^2)$.
%
%        In order to make cooperative game concepts practical in real world application, we have proposed an approximation multi-layer
%        algorithm useful for service oriented computing settings. Our excrements illustrate, these algorithms can provide
%        applicable and near optimal solutions for real world applications.

### 2014-03-04 seminar/seminar_report/chapter3.tex
changes

In this section, we discuss the parameters and preliminary
concepts that we use in the rest of the proposal.

\subsection{Architecture}

Our system consists of three main types of entities working
together:

\emph{1) Web services} are rational entities that aim to maximize
their utilities by providing high quality services to end users.
They aim to maximize their individual income by receiving enough
requests from end users. In order to increase their revenue, web
services seek for more tasks if they have the capacity and
throughput to do so. Web services can join communities to have
better efficiency by collaborating with others, to have access to
higher market share, and to have opportunity of receiving a bigger
task pool from end users. Throughout this proposal, in our
equations, we refer to web services as $ws$ and to the set of web
services hosted by a given community as $C$. To simplify the
notation, sometimes we simply write $ws$ instead of $ws \in C$ to
go through the elements $ws$ of the set $C$.

\emph{2) Master Web Services} or the community coordinators, are representatives of the
communities of web services and responsible for their management.
Communities receive requests from users and aim to host a healthy
set of web services to perform the required tasks. They seek to
maximize user satisfaction by having tasks accomplished according
to the desired QoS. In fact, higher user satisfaction will bring
more user requests and increase the market share and revenue of
the community.

\emph{3) Users} generate requests and try to find the best
available services. User satisfaction is abstracted as function of
quantity and quality of tasks accomplished by a given service.
Higher user satisfaction leads to higher trust of the community by users hence directing more requests towards that service provider.

\subsection{Web Service Parameters}\label{ws_parameters}

@@

\subsection{Web Service Communities}\label{webservice-communities}

Figure 3 represents our revised architecture of web service
communities where tasks are to be distributed among the members
that are interested in forming stable coalitions. As discussed in
Chapter 2, communities are essentially virtual platforms
aggregating web services having similar and complementary
functionalities and communicate with other entities such as UDDI
registries and users using particular protocols. Web services join
communities to increase their utility by having larger market
share and task pool. Community coordinators or master web services
are responsible for community development, managing membership
requests from web services and distributing user tasks among the
community members. Community coordinators try to attract quality
web services and keep the community as stable and productive as
possible to gain better reputation and user satisfaction, which
results in having higher revenue.

@@

As mentioned in Section \ref{webservice-communities}, communities
are robust service providers with well established market share
and reputation. By maintaining their reputation and performance,
they attract  end users which choose them as service providers to
perform their tasks. The community master is characterized by a
request rate $(R_C)$ from users. Each web service comes with a
given QoS ($QoS_{ws}$) from which the throughput $Th_{ws}$ is
excluded. Throughput is the average rate of tasks a web service
can perform per time unit. Its exclusion from $QoS_{ws}$ allows us
to build our analysis on the particular value of $Th_{ws}$. Thus,
web services perform tasks with an average output quality of
$QoS_{ws}$ and a throughput rate of $Th_{ws}$.

@@

In previous sections, our focus was on community formation and we the focus was on cooperative behaviour of the web services as agents. However competition within cooperative environments, for business agents having different set of capabilities. Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}. In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite. However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure. Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section. we propose a mechanism within which service agents
in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this paper interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task. We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate). In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility. We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.

@@

\begin{figure*}%[!t]
\centerline{\includegraphics[width=6.8in]{tax_dyn.eps}}
\caption{Analysis of community subsiding coefficient $\lambda$
having web service different stability levels of $\tau$ on average
community size, number of tasks performed, average quality of
service, and average cost/income of communities.}
\label{fig_dynamic_taxtation}
\end{figure*}

In the previous experiment, we considered the scenario where all
web services are stable, will not leave the group, and will
fulfill their promised QoS for a good period of time. However, in
real world scenarios of web services, this is not always the case.
This is the reason why the community coordinator would be interested in paying
web services in order to keep the group reliable from the end
user's point of view. In our next scenario, we have introduced the
new instability variable $\tau$ ranging from 0 to 1, 0 meaning web
services having no instability issues and will perform as they
claimed until the end of the experiment, and 1 meaning very
unstable web services, which will stop functioning on the first
iteration of the community distributing tasks. Figure
\ref{fig_dynamic_taxtation} illustrates the results of our
experiment having web services with average instability values of
0 to 0.5 and having relative subside value $\lambda$ of 1, 1.3,
1.6, and 2. The \emph{Cost/Income} charts on the right column show
that having subside value of 1.3 incurs the least cost and
increases the community income significantly. Subsiding values of
1.6 and 2 yield high cost to the community and only slightly
increase the community revenue. Moreover, the role of subsiding is
much more obvious when we have unstable web services. In scenarios
where web services are 100\% stable, the subsiding cost will
hardly be compensated by the community revenue.

@@

In this section, the objective is to investigate the effectiveness of the proposed strategic system in section \ref{s:coop}.

We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this report (referred to as coopetitive);
(2) a community that follows a stochastic reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive). 
%The proposed model's
%reasoning mechanism allows services to make decisions that
%maximize their utilities, so that if the service cannot compete,
%the procedure would suggest to collaborate, which is better than
%competing and failing to obtain the task. In this case, the service stays idle but
%still pays the community membership fee, which means losing
%utility. The developed strategic decision making mechanism leads
%some service agents to follow cooperative strategies that overall
%maintain an optimal community budget. In the same figure, we
%observe the cumulative budget of a community where services follow
%random interacting strategies. The outcome is clearly lower
%because services at each run randomly decide over their acting
%strategies. This potentially influences the community budget
%because a low quality service if randomly selects to follow the
%competitive strategy, it will fail to perform a task with high QoS
%requirements.

>>>>

Our system consists of three main types of entities working
together: \emph{1) Web services} are rational entities that aim to maximize
their utilities by providing high quality services to end users.
They aim to maximize their individual income by receiving enough
requests from end users. In order to increase their revenue, web
services seek for more tasks if they have the capacity and
throughput to do so. Web services can join communities to have
better efficiency by collaborating with others, to have access to
higher market share, and to have opportunity of receiving a bigger
task pool from end users. Throughout this proposal, in our
equations, we refer to web services as $ws$ and to the set of web
services hosted by a given community as $C$. 
%To simplify the
%notation, sometimes we simply write $ws$ instead of $ws \in C$ to
%go through the elements $ws$ of the set $C$.
\emph{2) Master Web Services} or the community coordinators, are representatives of the
communities of web services and responsible for their management.
Communities receive requests from users and aim to host a healthy
set of web services to perform the required tasks. They seek to
maximize user satisfaction by having tasks accomplished according
to the desired QoS. 
%In fact, higher user satisfaction will bring
%more user requests and increase the market share and revenue of
%the community. 
\emph{3) Users} generate requests and try to find the best
available services. User satisfaction is abstracted as function of
quantity and quality of tasks accomplished by a given service.
Higher user satisfaction leads to higher trust of the community by users hence directing more requests towards that service provider.

@@

Figure 3 represents our revised architecture of web service
communities where tasks are to be distributed among the members
that are interested in forming stable coalitions. As discussed in
Chapter 2, communities are essentially virtual platforms
aggregating web services having similar and complementary
functionalities and communicate with other entities such as UDDI
registries and users using particular protocols. Web services join
communities to increase their utility by having larger market
share and task pool. 
%Community coordinators or master web services
%are responsible for community development, managing membership
%requests from web services and distributing user tasks among the
%community members. Community coordinators try to attract quality
%web services and keep the community as stable and productive as
%possible to gain better reputation and user satisfaction, which
%results in having higher revenue.

@@

As mentioned in Section \ref{s:preliminaries}, communities
are robust service providers with well established market share
and reputation. By maintaining their reputation and performance,
they attract  end users which choose them as service providers to
perform their tasks. The community master is characterized by a
request rate $(R_C)$ from users. Each web service comes with a
given QoS ($QoS_{ws}$) from which the throughput $Th_{ws}$ is
excluded. Throughput is the average rate of tasks a web service
can perform per time unit. Its exclusion from $QoS_{ws}$ allows us
to build our analysis on the particular value of $Th_{ws}$. Thus,
web services perform tasks with an average output quality of
$QoS_{ws}$ and a throughput rate of $Th_{ws}$.

@@

In previous sections, our focus was on community formation and we emphasised on cooperative behaviour of the web services as agents. Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}. In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite. However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure. Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section. we propose a mechanism within which service agents
in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this paper interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task. We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate). In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility. We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.

@@

\begin{figure*}%[!t]In the previous experiment, we considered the scenario where all
web services are stable, will not leave the group, and will
fulfill their promised QoS for a good period of time. However, in
real world scenarios of web services, this is not always the case.
This is the reason why the community coordinator would be interested in paying
web services in order to keep the group reliable from the end
user's point of view.
\centerline{\includegraphics[width=6.8in]{tax_dyn.eps}}
\caption{Analysis of community subsiding coefficient $\lambda$
having web service different stability levels of $\tau$ on average
community size, number of tasks performed, average quality of
service, and average cost/income of communities.}
\label{fig_dynamic_taxtation}
\end{figure*}

In our next scenario, we have introduced the
new instability variable $\tau$ ranging from 0 to 1, 0 meaning web
services having no instability issues and will perform as they
claimed until the end of the experiment, and 1 meaning very
unstable web services, which will stop functioning on the first
iteration of the community distributing tasks. Figure
\ref{fig_dynamic_taxtation} illustrates the results of our
experiment having web services with average instability values of
0 to 0.5 and having relative subside value $\lambda$ of 1, 1.3,
1.6, and 2. The \emph{Cost/Income} charts on the right column show
that having subside value of 1.3 incurs the least cost and
increases the community income significantly. Subsiding values of
1.6 and 2 yield high cost to the community and only slightly
increase the community revenue. Moreover, the role of subsiding is
much more obvious when we have unstable web services. In scenarios
where web services are 100\% stable, the subsiding cost will
hardly be compensated by the community revenue.

@@

In this section, the objective is to investigate the effectiveness of the proposed strategic system in section \ref{s:coop}.
We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this report (referred to as coopetitive);
(2) a community that follows a stochastic reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive).
%The proposed model's
%reasoning mechanism allows services to make decisions that
%maximize their utilities, so that if the service cannot compete,
%the procedure would suggest to collaborate, which is better than
%competing and failing to obtain the task. In this case, the service stays idle but
%still pays the community membership fee, which means losing
%utility. The developed strategic decision making mechanism leads
%some service agents to follow cooperative strategies that overall
%maintain an optimal community budget. In the same figure, we
%observe the cumulative budget of a community where services follow
%random interacting strategies. The outcome is clearly lower
%because services at each run randomly decide over their acting
%strategies. This potentially influences the community budget
%because a low quality service if randomly selects to follow the
%competitive strategy, it will fail to perform a task with high QoS
%requirements.

### 2014-03-04 seminar/seminar_report/chapter5.tex
changes

\setcounter{chapter}{3}
\chapter{Conclusion and Future Work}\label{sec:conclusionfuturework}
In this chapter, we describe the phases of our plan for exploring
the research challenges and investigating the research issues
identified in Chapter 3. This chapter also includes research
methodology and future publication plan.

\section {Conclusion}

@@

\item Applying other valuation function in our scenarios using for
instance Weighted Voting Games (WCG) in order to develop a
multiple weighted algorithm to find best coalition structures
satisfying different weights on each community.

@@

\item Developing an approximation algorithm for shapely value
payoff distribution vector in community setting.

\item Developing a community membership algorithm technique for
our agents in "incomplete information" settings.

>>>>

\setcounter{chapter}{3}
\chapter{Conclusion and Future Work}\label{sec:conclusionfuturework}

@@

@@

\item Developing a community membership algorithm technique for
our agents in more distributed and "incomplete information" settings.
